MapReduce to My Ears\\ {\Large Using Big Data for Music Synthesis}

### 2013-05-10 writeup/paper.tex
fixups on explanation in paper for mapper

After taking the image data to an intermediate format, we must map the
image data to a set of note / region pairs for use in the MIDI.  To do
this, we map a conversion function across each of the different
portions of each image.  The conversion happens by mapping over our
set of images in the \code{Image2MusicMR} class.  The input of this
reducer is a set of key/value pairs which constitute the image number
and image data (a set of integers representing each pixel in the
image).  The output of the image to music conversion is $n$ sets of
note lists (where notes are expressed as pairs).  This is stored as a
set of key/value pairs where the key is the region number and image
number pair (subsequently discussed, but used for secondary sorting)
and the part number and MIDI note.

>>>>

After taking the image data to an intermediate format, we must map the
image data to a set of note / region pairs for use in producing MIDI
output.  To do this, we map a conversion function across each region
of each image.  The conversion happens by mapping over our set of
images in the \code{Image2MusicMR} class.  The input of this mapper is
a set of key/value pairs which constitute the image number and image
data (a set of integers representing each pixel in the image).  The
output of the image to music conversion is $n$ sets of note lists
(where notes are expressed as pairs).  The reducer takes each part of
the sore and combines it into a resulting MIDI file.  This is stored
as a set of key/value pairs where the key is the region number and
image number pair (subsequently discussed, but used for secondary
sorting) and the part number and MIDI note.
